### 2017-11-10 Draft2/Indexing.Growth.tex
Replace Var with Lcl for algo local variables
Algos: Variables for param names
Algos: Add spaces between commas
More work (might be a long shot to get this finished on time)

\begin{algorithm}
	\begin{algorithmic}
		\Function{$\FuncGetItem$}{$\VarList, index$}
			\State $\VarIndex \gets index$
			\For{$\VarBuffer \TextIn \VarList.\FieldTail$}
				\If{$\VarIndex < \VarBuffer.\FieldLength$}
					\State \Return $\VarBuffer[\VarIndex]$
				\EndIf
				\State $\VarIndex \gets \VarIndex - \VarBuffer.\FieldLength$
			\EndFor
			\State \Return $\VarList.\FieldHead[\VarIndex]$
		\EndFunction
	\end{algorithmic}
\end{algorithm}

@@

I define a helper function, $\FuncGetBuffer$, that gets the buffer associated with a given $\VarIndexBuffer$:

% Todo: Make parameter names for other parts consistent.
\begin{algorithm}
	\begin{algorithmic}
		\Function{$\FuncGetBuffer$}{$\VarList, \VarIndexBuffer$}
			\If{$\VarIndexBuffer < \VarList.\FieldTail.\FieldSize$}
				\State \Return $\VarList.\FieldTail[\VarIndexBuffer]$
			\Else
				\State \Return $\VarList.\FieldHead$
			\EndIf
		\EndFunction
	\end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}
	\begin{algorithmic}
		\Function{$\FuncGetItem$}{$\VarList, index$}
			\State $(\VarIndexBuffer, \VarIndexElement) \gets \FuncDecompose(index)$
			\State \Return $\VarList.\FuncGetBuffer(\VarIndexBuffer)[\VarIndexElement]$
		\EndFunction
	\end{algorithmic}
\end{algorithm}

The task is now to find formulae for $\VarIndexBuffer$ and $\VarIndexElement$ in terms of $i$.

>>>>

\begin{algorithm}
	\begin{algorithmic}
		\Function{$\FuncGetItem$}{$\VarList,\ \ParamIndex$}
			\State $\LclIndex \gets \ParamIndex$
			\For{$\LclBuffer \TextIn \VarList.\FieldTail$}
				\If{$\LclIndex < \LclBuffer.\FieldLength$}
					\State \Return $\LclBuffer[\LclIndex]$
				\EndIf
				\State $\LclIndex \gets \LclIndex - \LclBuffer.\FieldLength$
			\EndFor
			\State \Return $\VarList.\FieldHead[\LclIndex]$
		\EndFunction
	\end{algorithmic}
\end{algorithm}

@@

I define a helper function, $\FuncGetBuffer$, that gets the buffer associated with a given $\VarIndexBuffer$. $\VarIndexBuffer$ is assumed to be valid; that is, $0 \leq \VarIndexBuffer \leq \VarNumItemsTail$.

% Todo: Make parameter names for other parts consistent.
\begin{algorithm}
	\begin{algorithmic}
		\Function{$\FuncGetBuffer$}{$\VarList,\ \LclIndexBuffer$}
			\If{$\LclIndexBuffer < \VarList.\FieldTail.\FieldSize$}
				\State \Return $\VarList.\FieldTail[\LclIndexBuffer]$
			\Else
				\State \Return $\VarList.\FieldHead$
			\EndIf
		\EndFunction
	\end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}
	\begin{algorithmic}
		\Function{$\FuncGetItem$}{$\VarList,\ \ParamIndex$}
			\State $(\LclIndexBuffer,\ \LclIndexElement) \gets \FuncDecompose(\ParamIndex)$
			\State \Return $\VarList.\FuncGetBuffer(\LclIndexBuffer)[\LclIndexElement]$
		\EndFunction
	\end{algorithmic}
\end{algorithm}

% Todo: \VarLogicalIndex for i? Introduce "logical index" term above?
The task is now to find formulae for $\VarIndexBuffer$ and $\VarIndexElement$ in terms of $i$, in order to implement $\FuncDecompose$.

% Todo: There's an awful lot of lemmas. Make some into theorems.
\begin{lemma}
	The formulae for $\VarIndexBuffer$ and $\VarIndexElement$ are
	\begin{align*}
	\VarIndexBuffer &= \VarUseful|_{n = i + 1}\\
	\VarIndexElement &= i - \VarGrowSeq_{\VarIndexBuffer - 1}
	\end{align*}
\end{lemma}

% Todo: "As shown earlier"
% Todo: Again, by convention \VarGrowSeq_{-1} = 0. Modify the algorithm accordingly.
\begin{proof}
	Appending new items does not change the index of an item that is already in the list. Thus, this problem can be reduced to finding the last element when $n = i + 1$.

	The last element always resides in the head, so $\VarIndexBuffer = \VarNumItemsTail|_{n = i + 1}$. As shown earlier, $\VarNumItemsTail = \VarUseful$, so $\VarIndexBuffer = \VarUseful|_{n = i + 1}$.

	To find $\VarIndexElement$, consider the equation:
	\begin{align*}
	n = \text{\# of items in tail} + \text{\# of items in head}
	\end{align*}
	From the premise, $n = i + 1$. The number of items in the tail is the last size at which $\FuncGrow$ was called, or $\VarGrowSeq_{\VarUseful - 1} = \VarGrowSeq_{\VarIndexBuffer - 1}$. Finally, since the desired item is the last item in the growth array, it is also the last item in the head. Then the size of the head is $\VarIndexElement + 1$. Substituting these values into the above equation, I receive
	\begin{align*}
	i + 1 &= \VarGrowSeq_{\VarIndexBuffer - 1} + \VarIndexElement + 1\\
	\VarIndexElement &= i - \VarGrowSeq_{\VarIndexBuffer - 1}
	\end{align*}
	completing the proof.
\end{proof}

% Todo: Mention formulae for \VarUseful and \VarGrowSeq_{\VarIndexBuffer - 1}.
Now, the $\FuncDecompose$ function can be implemented as follows:

% Todo: Continue to consider usage of mathematical vs. algorithm vars.
% Todo: Can ceiling of \log_2 be implemented fast? Also, what if \VarInitCapacity is not a power of 2?
\begin{algorithm}
	\begin{algorithmic}
		\Function{$\FuncDecompose$}{$\ParamIndex$}
			\State $\LclIndexBuffer \gets \max(\left\lceil \log_{\VarGrowthFactor} (i + 1) - \log_{\VarGrowthFactor} \VarInitCapacity \right\rceil, 0)$
			\State $\LclIndexElement \gets \ParamIndex - \VarGrowthFactor^{\LclIndexBuffer - 1} \times \VarInitCapacity$
			\State \Return $(\LclIndexBuffer,\ \LclIndexElement)$
		\EndFunction
	\end{algorithmic}
\end{algorithm}

Clearly, $\FuncDecompose$ runs in constant time. At first glance, however, it appears to be quite expensive since it % Bookmark
